The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-23 paper/ms.tex
reviewer thank
correction
caldwell comments

@@

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD, which successively shuffles each row of pixels to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.

@@

>>>>

\author[0000-0003-1963-9616]{Douglas A. Caldwell}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}

@@

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Twelve rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, twelve `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. Compared to the flux in the science image for a given target, the masked and virtual smear rows each receive an incident flux in proportion to the relative exposure times of the smear versus imaging pixels:  $\sim (0.52\,\text{s}/1070\,\text{rows})/6.2\,\text{s}$. If the smear flux is dominated by the light from a single star, the combined flux from the 24 smear rows is equivalent to the normal flux of a star $\sim 6.8$ magnitudes fainter.

@@

We would like to thank the anonymous reviewer, whose comments significantly improved this paper.
